Verifying Demonstrations

### 2021-06-16 paper/protocol.tex
Makes subfigures tiny to fit next to each other
Updates data in adversary model
Clarifies intro to protocol

The entities involved in our protocol are participants and (count) verifiers.
A participant can assume three different roles:
\begin{enumerate}
\item The \emph{organizer} has written a manifesto for the protest and 
  disseminated it to others.
\item A \emph{protester} is attending the protest and asks witnesses to vouch 
  for their presence.
\item A \emph{witness} provides proofs to protesters which state that they indeed participated, constructed such that the proofs are verifiable by 
  third parties.
\end{enumerate}
In general, there is one organizer and every participant can act as
either or both protester and witness.

After the protest, anyone can count the number of participants (of the protest and the
protocol) and verify anyone else's count given the relevant meta data
(which protest, location, time, and witness parameters used in the
count). We refer to anyone counting or verifying a count as the
verifier; the process is the same.

@@

To count or verify the participation count for a protest \(\prtst\) with 
identifier \(\cid_0\), a verifier must download the set \(\pshs_{\cid_0}\) of 
all \(s_P\) and \(s_W\) tuples containing \(\cid_0\) from the ledger~\(\TS\).
Then from \(\pshs_{\cid_0}\), a verifier can build, in succession,
\begin{enumerate*}
\item the valid proof shares \(s_j^{(i)}\) for all matching pairs \((s_P, 
    s_W)\) corresponding to a witness \(i\) and a protester \(j\),
\item the participation proof \(\prf_{j}\) for each protester \(j\),
\item the set \(\prfs_{\prtst}^{\str,\theta}\) of eligible participation proofs 
  for all protesters in \(\prtst\), and finally,
\item the participation count, \ie the cardinality of 
  \(\prfs_\prtst^{\str,\theta}\).
\end{enumerate*}

>>>>

The entities involved in our protocol are participants and (count) verifiers.
A participant can assume three different roles:
\begin{enumerate}
\item The \emph{organizer} has written a manifesto for the protest and 
  disseminated it to others.
  Anyone can do this, but in general, there is only one organizer.
\item A \emph{protester} is attending the protest and asks witnesses to vouch 
  for their presence.
\item A \emph{witness} provides proofs to protesters which state that they indeed participated, constructed such that the proofs are verifiable by 
  third parties.
\end{enumerate}
After the protest, anyone can be a verifier (universal verifiability, 
\cref{security-properties}), \ie count the number of participants (of the 
protest and the protocol) or verify anyone else's count given the relevant meta 
data (which protest, location, time, and witness parameters used in the
count). We refer to anyone counting or verifying a count as the
verifier; the process is the same.

@@

To count or verify the participation count for a protest \(\prtst\) with 
identifier \(\cid_0\), a verifier must download the set \(\pshs_{\cid_0}\) of 
all \(s_P\) and \(s_W\) tuples containing \(\cid_0\) from the ledger~\(\TS\).
Then from \(\pshs_{\cid_0}\), a verifier can build, in succession,
\begin{enumerate*}
\item the valid proof shares \(s_j^{(i)}\) for all matching pairs \((s_P, 
    s_W)\) corresponding to a witness \(i\) and a protester \(j\),
\item the participation proof \(\prf_{j}\) for each protester \(j\),
\item the set \(\prfs_{\prtst}^{\str,\theta}\) of eligible participation proofs 
  for all protesters in \(\prtst\), and finally,
\item the participation count, \ie the cardinality of 
  \(\prfs_{\prtst}^{\str,\theta}\).
\end{enumerate*}
